Attract and kill: Spinosad containing spheres to control onion maggot (\textit{Delia antiqua})

### 2020-01-06 manuscript/pest-management-science/reviewer-response/reviewer-response.tex

Line 68-69: This was already state above, seems redundant.

\begin{quote}
    \textit{Thanks for mentioning this.  We have removed the redundant statement.  }
\end{quote}

Line 71: More details are needed: how many reps/field, how many fields, how much distance between spheres, etc. Where in the field relative to the crop were spheres? What were they placed on and how high?

\begin{quote}
    \textit{Thanks for the opportunity to elaborate.  Details about reps, fields, distances, location, and height have been included on lines ....}
\end{quote}

\begin{quote}
    \textit{Thanks for the suggestions.  Information on the timing of the experiment has been added to line.... Units have also been changed to SI.  Details have also been added regarding replications and field sites (lines ...).  }
\end{quote}

\begin{quote}
    \textit{This was indeed based on previous work establishing the attractiveness of the spheres (Willett et al 2019). }
\end{quote}

\begin{quote}
    \textit{New but not novel.  It differed from previous formulations with the addition of the two extra components included below.  We have elaborated on the reasons for developing this on lines.   }
\end{quote}

Line 100: why were these compounds chosen?

\begin{quote}
    \textit{Excellent question.  The thought was that these compounds would help sterilize the paraffin mixture and enhance performance of the spheres over the long term.  }
\end{quote}

Line 104: was this true for previous experiments as well? If yes, please mention above.

\begin{quote}
    \textit{This was indeed true for previous experiments as well.  Thanks for the suggestion; these details have been included in the sections above as well.  }
\end{quote}

Line 108: which years?

\begin{quote}
    \textit{Great question.  This information has been included and elaborated upon in all methods sections on lines...}
\end{quote}

Line 110: pls explain how it was analyzed in addition to how it was displayed.

\begin{quote}
    \textit{Thanks for your inquiry.  It was analyzed using a smoothing function consisting of a generalized additive model with cubic splines.  }
\end{quote}

Line 112: aren't these the same thing?

\begin{quote}
    \textit{Thanks for your question.  Yes and No.  While linear models and analysis of variance use the same underlying model structure, they have two different objectives and answer two different questions.  Linear models represent the relationship between independent and dependent variables.  Analysis of variance compares inter and intra-group variation to examine differences.  In our case, both approaches were used because we are interested both in modeling relationships and differences between groups.  }
\end{quote}

Line 113: I'd like to get more details about which factors you have used, fixed and random.

@@

\begin{quote}
    \textit{Thanks for your question.  Yes and No.  While linear models and analysis of variance use the same underlying model structure, they have two different objectives and answer two different questions.  Linear models represent the relationship between independent and dependent variables.  Analysis of variance compares inter and intra-group variation to examine differences.  In our case, both approaches were used because we are interested both in modeling relationships and differences between groups.  }
\end{quote}

Line 113: I'd like to get more details about which factors you have used, fixed and random.

\begin{quote}
    \textit{}
\end{quote}

Line 115: AIC?, BIC? How did you use these to inform model selection? Considerations: third time this word is used in this sentence.

Line 116:  I suggest rewording this sentence. I'm assuming that you are talking about means separation here?

Why use both, why not just one or the other? be more explicit about which model goes with what data. I'd like to see a list of dependent and independent variables and fixed and random effects.I suggest removing such a blanket statement and being more specific as I mentioned above.

Line 124: need to mention these where you talk about how you built and selected models. These are the tools you used to do that.

Line 128: I'm not following why showing this data is relevant. You also have not done analysis on it. Suggest incorporating it into the rest of the MS effectively.

Line 129: What period was this? Be more specific

Line 130: how were they sexed? Mention in the methods.

Line 131: delete "roughly"

Line 133: What do you mean? Significantly different? Different from what?

\end{document}

### 2020-01-06 manuscript/pest-management-science/main.tex
More reviewer comments... :)

To do so, the ability of spinosad spheres to kill \textit{D. antiqua} flies was evaluated over the course of 2006 and 2007 field seasons by deploying a cohort of spheres containing spinosad at the beginning of the season (mid May) and recovering a subset of them on a monthly basis to evaluate weather exposure and dose effects.  Following initial deployment in mid May spheres were recovered in mid June, mid July, mid August, and mid September resulting in cohorts exposed to field conditions for 1 month, 2 months, 3 months, 4 months, respectively. Deployment in the field followed a randomized controlled block design.

Following recovery from the field, spheres were photographed to document degradation, then each one was immediately suspended in 25cm x 25cm x 50cm screen and plexiglass cages containing water in a petri dish. Ten male and ten female \textit{D. antiqua} flies were then introduced to each cage and mortality monitored every 24 hours for 72 hours. This trial was conducted for both spinosad containing and control spheres. Six replications of each of the 12 treatments (3 spinosad levels x 4 periods of field exposure) were conducted.

@@

To evaluate the efficacy of attract and kill techniques for reducing \textit{D. antiqua} larval damage, onions killed or damaged by \textit{D. antiqua} larvae were monitored throughout the field seasons of 2007 and 2008. Onion seed of \textit{Allium cepa} L. ’Arsenal’, an early yellow globe variety, was planted in late April with plants subjected to treatments in a randomized controlled block design with six replicates across three field sites.  Six treatment combinations were evaluated (i.e., insecticide-treated plants only [positive control], non-insecticide treated plants with spinosad containing white spheres only, non-insecticide treated plants with spinosad containing white spheres and Delia Lure, non-insecticide treated plants with white sticky cards only, non-insecticide treated plants with white sticky cards and Delia Lure, and non-insecticide treated plants only [negative control]).  Insecticide-treated plants were grown from seeds treated with the FarMore FI500 seed treatment package. This treatment was included in the experiment to be a positive control. Non-insecticide treated plants were grown from fungicide-only treated seeds and did not receive any attract and kill strategies. Spinosad spheres containing 0.5\% spinosad were deployed with and without attractive Delia Lures (AgBio, Westminster, CO) as an attract and kill solution. White sticky cards with and without attractive Delia Lure were also deployed.

@@

To enhance attractiveness, longevity, and performance of spinosad containing spheres, a new formulation of spinosad containing sphere was developed with 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate. The efficacy of this new formulation was compared with spheres containing just 0.5\% spinosad and no spinosad controls in field cage trials in 2008. Treatments were deployed in a randomized controlled block design with four replications and each individual plot consisted of four rows of onion each 3.7m (12ft)  long. All onion seeds including those in the untreated control were treated with fungicides: thiram (Thiram 42 S {@}188 mg a.i./ 100 g seed) and tebuconazole (Raxil 2.6 F @ 250 mg a.i. / 100 g seed). Seeds were planted in early May and each plot was caged (3.7m x 3.7m x 2m) using PVC pipe and screen mesh. One hundred fifty \textit{D. antiqua} flies with a 50:50 male to female ratio were released into each cage on the second of June and again nine days later on June 11th. As described above, initial and final stand counts were taken and plant damage due to \textit{D. antiqua} larvae evaluated on a weekly basis.

>>>>

To do so, the ability of spinosad spheres to kill \textit{D. antiqua} flies was evaluated over the course of 2006 and 2007 field seasons by deploying a cohort of spheres containing spinosad at the beginning of the season (mid May) and recovering a subset of them on a monthly basis to evaluate weather exposure and dose effects.  Following initial deployment in mid May spheres were recovered in mid June, mid July, mid August, and mid September resulting in cohorts exposed to field conditions for 1 month, 2 months, 3 months, 4 months, respectively. Deployment in the field followed a randomized controlled block design with six replicates of the 12 treatments (3 spinosad levels x 4 periods of field exposure) across three field sites from 2006 to 2007.  Spheres were suspended from 30cm long stakes placed along the long side of the onion field at a spacing of 15.2m.

Following recovery from the field, spheres were photographed to document degradation, then each one was immediately suspended in 25cm x 25cm x 50cm screen and plexiglass cages containing water in a petri dish. Ten male and ten female \textit{D. antiqua} flies were then introduced to each cage and mortality monitored every 24 hours for 72 hours. This trial was conducted for both spinosad containing and control spheres.

@@

To evaluate the efficacy of attract and kill techniques for reducing \textit{D. antiqua} larval damage, onions killed or damaged by \textit{D. antiqua} larvae were monitored throughout the field seasons of 2007 and 2008. Onion seed of \textit{Allium cepa} L. ’Arsenal’, an early yellow globe variety, was planted in late April with plants subjected to treatments in a randomized controlled block design with six replicates across three field sites.  Six treatment combinations were evaluated (i.e., insecticide-treated plants only [positive control], non-insecticide treated plants with spinosad containing white spheres only, non-insecticide treated plants with spinosad containing white spheres and Delia Lure, non-insecticide treated plants with white sticky cards only, non-insecticide treated plants with white sticky cards and Delia Lure, and non-insecticide treated plants only [negative control]).  Insecticide-treated plants were grown from seeds treated with the FarMore FI500 seed treatment package. This treatment was included in the experiment to be a positive control. Non-insecticide treated plants were grown from fungicide-only treated seeds (thiram [Thiram 42 S {@}188 mg a.i./ 100 g seed] and tebuconazole [Raxil 2.6 F @ 250 mg a.i. / 100 g seed]) and did not receive any attract and kill strategies. Spinosad spheres containing 0.5\% spinosad were deployed with and without attractive Delia Lures (AgBio, Westminster, CO) as an attract and kill solution. White sticky cards with and without attractive Delia Lure were also deployed.

@@

To enhance attractiveness, longevity, and performance of spinosad containing spheres, a new formulation of spinosad containing sphere was developed with 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate to stabilize the paraffin and improve performance. The efficacy of this new formulation was compared with spheres containing just 0.5\% spinosad and no spinosad controls in field cage trials in 2008. Treatments were deployed in a randomized controlled block design with four replications and each individual plot consisted of four rows of onion each 3.7m (12ft)  long. All onion seeds including those in the untreated control were treated with fungicides: thiram (Thiram 42 S {@}188 mg a.i./ 100 g seed) and tebuconazole (Raxil 2.6 F @ 250 mg a.i. / 100 g seed). Seeds were planted in early May and each plot was caged (3.7m x 3.7m x 2m) using PVC pipe and screen mesh. One hundred fifty \textit{D. antiqua} flies with a 50:50 male to female ratio were released into each cage on the second of June and again nine days later on June 11th. As described above, initial and final stand counts were taken and plant damage due to \textit{D. antiqua} larvae evaluated on a weekly basis.
